Contracts for unions and intersections are hard for Nickel

### 2021-05-20 paper.tex
Small fixes unions section

\subsection*{Unions}
Unions are fundamental building blocks of programs. A union holds a value whose
shape is known to be in a fixed set of alternatives: for example, a value that
can be either a boolean or a string. They corresponds logically to conjunctions.
Used in combination with products, they can represent arbitrary tree-like
structures, allowing to model a large class of data
(\ref{fig:union-adt-ex}).

@@

Other use-cases for unions include:
\begin{itemize}
    \item To represent nullable values in JSON (\ref{fig:union-nullable-ex}).
    \item For plain enumerations (\ref{fig:union-enum-ex}).
    \item To support different representations of the same data
        (\ref{fig:union-alt-ex}).
\end{itemize}
All of which are useful in a configuration language.

>>>>

\subsection*{Unions}
Unions are fundamental building blocks of programs. A union holds a value whose
shape is known to be in a fixed set of alternatives: for example, a value that
can be either a boolean or a string. They correspond logically to conjunctions.
Used in combination with products, they can represent arbitrary tree-like
structures, allowing to model a large class of data
(\ref{fig:union-adt-ex}).

@@

In addition to internal program representations, unions are also useful to model
external data:
\begin{itemize}
    \item To represent nullable values(\ref{fig:union-nullable-ex}).
    \item For plain enumerations (\ref{fig:union-enum-ex}).
    \item To support different representations of the same data
        (\ref{fig:union-alt-ex}).
\end{itemize}
All of which are common in configurations.
